An Empirical Study of Invasion and Resistance for Iterated Prisoner's Dilemma Strategies

### 2017-05-26 main.tex
Adjust wording.

The results for \(x_{N/2}\) show similarities to the results for \(x_{N-1}\) and
in particular TF1, TF2 and TF3 all rank in the top 8 strategies. This is to be
expected since, as described in Section~\ref{sec:strategies} these strategies
were trained in an initial population of \(N/2\) individuals.

>>>>

The results for \(x_{N/2}\) show similarities to the results for \(x_{N-1}\) and
in particular TF1, TF2 and TF3 ranked one, three and eight. This is to be
expected since, as described in Section~\ref{sec:strategies} these strategies
were trained in an initial population of \((N/2, N/2)\) individuals.
